---
title: "p8105_hw1_sy3269"
author: Soomin You
date: 2024-09-13
output: github_document
---


## Problem 0.1 and 0.2

This repo is for P8105 Homework 1. 

```{r message = FALSE}
library(tidyverse)
```

I loaded necessary packages (e.g. `tidyverse`).

## Problem 1

```{r data summary}
data("penguins", package = "palmerpenguins")
p_variable = names(penguins)
p_row = nrow(penguins)
p_col = ncol(penguins)
```

There are `r length(p_variable)` variables in penguins dataset. 

Names of the variables are `r p_variable`.

There are `r p_row` rows and `r p_col` columns. 

```{r flipper}
p_flipper = na.omit(penguins$flipper_length_mm)
mean_p_flipper = mean(p_flipper)
```

The mean flipper length of this penguin dataset is `r mean_p_flipper` mm. 

```{r plot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + 
  geom_point()

ggsave("penguin scatterplot.pdf")
    
```
This is a scatterplot of the penguins dataset where x = bill_length_mm and y = flipper_length_mm. 

The color will be added later. 