---
title: "p8105_hw1_sy3269"
author: Soomin You
date: 2024-09-18
output: github_document
---

## Problem 0.1 and 0.2

This repo is for P8105 Homework 1. 

```{r message = FALSE}
library(tidyverse)
```

I loaded necessary packages (e.g. `tidyverse`).

## Problem 1

```{r data summary}
data("penguins", package = "palmerpenguins")
p_variable = names(penguins)
p_row = nrow(penguins)
p_col = ncol(penguins)

p_species = count(penguins, species)
```

There are `r length(p_variable)` variables in penguins dataset and the names are `r p_variable`.

There are `r count(p_species)` species in the dataset and the names are `r pull(p_species,species)`.

There are `r p_row` rows and `r p_col` columns. 


```{r flipper}
p_clean = na.omit(penguins)
mean_p_flipper = mean(p_clean[["flipper_length_mm"]])
```

Missing data were removed first to make a clean penguins dataset. Then the mean flipper length of the clean dataset was found to be `r mean_p_flipper` mm. 

```{r plot}
ggplot(p_clean, aes(x = bill_length_mm, y = flipper_length_mm, color = (species))) + 
  geom_point()

ggsave("penguin scatterplot.pdf")
```

This is a scatterplot of the clean penguins dataset where x = bill_length_mm and y = flipper_length_mm. The different species are noted in different colors. 


## Problem 2 

```{r}
my_df = 
  tibble(
    norm_samp = rnorm(10), 
    vec_log =  norm_samp > 0, 
    vec_char = c("apple", "banana", "cherry", "date", "eggplant", "fig", "grape", "honey", "iceberg", "jujube"),
    vec_factor = factor(c("A", "B", "C", "A", "B", "C", "A", "B", "C", "A"))
  )
```

I created a data frame comprised of a *random sample* of size 10 from a standard Normal distribution, a *logical vector* indicating indicating whether elements of the sample are greater than 0, a *character vector* of length 10, and a *factor vector* of length 10, with 3 different factor “levels”. 


```{r}
my_df_vec_log = pull(my_df, vec_log)
my_df_vec_char = pull(my_df, vec_char)
my_df_vec_factor = pull(my_df, vec_factor)

mean(my_df_vec_log)
mean(my_df_vec_char)
mean(my_df_vec_factor)
```

Attempt to take the mean of each variable in my data frame was made. For logical vector, mean was calculated because **TRUE** and **FALSE** correspond to **1** and **0**. However, for character vector and factor vector, the mean could not be calculated because they were not *numeric* or *logical*. 

```{r, message = FALSE}
my_df_vec_log_num = as.numeric(my_df_vec_log)
my_df_vec_char_num = as.numeric(my_df_vec_char)
my_df_vec_factor_num = as.numeric(my_df_vec_factor)

```

Attempt to convert the variables to *numeric* type was made. The logical and factor variables were converted to *numeric* but the character vector could not be converted. ? 

