---
title: "p8105_hw1_sy3269"
author: Soomin You
date: 2024-09-18
output: github_document
---

## Problem 0.1 and 0.2

This repo is for P8105 Homework 1. 

```{r message = FALSE}
library(tidyverse)
```

I loaded necessary packages (e.g. `tidyverse`).

## Problem 1

```{r data summary}
data("penguins", package = "palmerpenguins")
p_variable = names(penguins)
p_row = nrow(penguins)
p_col = ncol(penguins)

p_species = count(penguins, species)
```

There are `r length(p_variable)` variables in penguins dataset and the names are `r p_variable`.

There are `r count(p_species)` species in the dataset and the names are `r pull(p_species,species)`.

There are `r p_row` rows and `r p_col` columns. 


```{r flipper}
p_clean = na.omit(penguins)
mean_p_flipper = mean(p_clean[["flipper_length_mm"]])
```

Missing data were removed first to make a clean penguins dataset. Then the mean flipper length of the clean dataset was found to be `r mean_p_flipper` mm. 

```{r plot}
ggplot(p_clean, aes(x = bill_length_mm, y = flipper_length_mm, color = (species))) + 
  geom_point()

ggsave("penguin scatterplot.pdf")
```

This is a scatterplot of the clean penguins dataset where x = bill_length_mm and y = flipper_length_mm. The different species are noted in different colors. 