---
title: "p8105_hw1_sy3269"
author: Soomin You
date: 2024-09-19
output: github_document
---

## Problem 0.1 and 0.2

This repo is for P8105 Homework 1. 

```{r message = FALSE}
library(tidyverse)
```

I loaded necessary packages (e.g. `tidyverse`).

## Problem 1

```{r, summary}
data("penguins", package = "palmerpenguins")
penguin_var = names(penguins) 
```

There are `r length(penguin_var)` variables in the penguins data set and the names are `r penguin_var`. 

*species*, *island*, *sex* and *year* are categorical variables, or factor vectors.

*bill_length_mm*, *bill_depth_mm* *flipper_length_mm* and *body_mass_g* are continuous variables.  The first two are identified as double vectors whereas the latter two are identified as integer vectors. 

The data set has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 


```{r, flipper}
mean_flipper = 
  drop_na(penguins, flipper_length_mm) |>
  pull(flipper_length_mm) |>
  mean()
```

Missing data in *flipper_length_mm* column were removed first. Then the mean flipper length was found. 
The mean flipper length is `r mean_flipper` mm. 



```{r, plot}
clean_penguins = drop_na(penguins, flipper_length_mm)

ggplot(clean_penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = (species))) + 
  geom_point()

ggsave("penguin scatterplot.pdf")
```

All missing data in penguins data set were removed before plotting. 

This is a scatterplot of the clean penguins data set where x = bill_length_mm and y = flipper_length_mm. The different species are noted in different colors. 


## Problem 2 

```{r}
my_df = 
  tibble(
    norm_samp = rnorm(10), 
    vec_log =  norm_samp > 0, 
    vec_char = c("apple", "banana", "cherry", "date", "eggplant", "fig", "grape", "honey", "iceberg", "jujube"),
    vec_factor = factor(c("A", "B", "C", "A", "B", "C", "A", "B", "C", "A"))
  )

my_df
```

I created a data frame comprised of a *random sample* of size 10 from a standard normal distribution, a *logical vector* indicating indicating whether elements of the sample are greater than 0, a *character vector* of length 10, and a *factor vector* of length 10, with 3 different factor “levels”. 


```{r}
norm_samp_mean = 
  pull(my_df, norm_samp) |>
  mean()

vec_log_mean = 
  pull(my_df, vec_log) |>
  mean()

vec_char_mean = 
  pull(my_df, vec_char) |>
  mean()

vec_factor_mean = 
  pull(my_df, vec_factor) |>
  mean()

norm_samp_mean 
vec_log_mean 
vec_char_mean
vec_factor_mean
```

Attempt to take the mean of each variable in my data frame was made. 

For random sample, the mean was calculated because it is a numeric vector.  

For logical vector, mean was calculated because **TRUE** and **FALSE** each correspond to **1** and **0**. So the mean gives a proportion of TRUE, or 1 in the vector. 

However, for character vector and factor vector, the mean could not be calculated. Mathematical operations can be performed only on *numeric* or *logical* variables. 

```{r, message = FALSE}
vec_log_num = 
  pull(my_df, vec_log) |>
  as.numeric()

vec_char_num = 
  pull(my_df, vec_char) |>
  as.numeric()
  
vec_factor_num = 
  pull(my_df, vec_factor) |>
  as.numeric() 
  
```

Attempt to convert the variables to *numeric* type was made. 

The *logical variable* was converted to numeric because **TRUE** and **FALSE** respecitvely correspond to **1** and **0** in R. 

The *character vector* could not be converted to numeric because characters do not have a direct numeric value. Unless representation of each character value is input, R cannot convert text strings to numeric values. 

The *factor vector* was converted to numeric because different levels in the factor vector correspond to numeric values. 


This helps explain why the mean could not calculated for some of the vectors. 
